What are the contributing factors to poor mental health in U.S?

### 2022-03-21 outputs/paper/paper.Rmd
change file path

Additionally, you can scan this QR code:
![QR Code for the survey](C:/Users/Isfan/Desktop/Supplemental Survey Screen Shots/QR CODE.png){width=20% height=20%}\

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('("../../outputs/paper/supplemental survey/001.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('("../../outputs/paper/supplemental survey/002.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('("../../outputs/paper/supplemental survey/003.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('("../../outputs/paper/supplemental survey/004.png')
```

>>>>

Additionally, you can scan this QR code:
![QR Code for the survey](supplemental_survey/QR_CODE.png){width=20% height=20%}\

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('supplemental_survey/001.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('supplemental_survey/002.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('supplemental_survey/003.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('supplemental_survey/004.png')
```
